Drake Plan

### 2019-08-26 R/drake_plan_conus.Rmd
slight revise[drake_plan_conus] check drake version

# Libraries
suppressPackageStartupMessages({
  library(sf)
  library(magrittr)
  library(drake)
  library(data.table)
  library(fst)
  library(future)
  library(here)
  library(nngeo)
  library(ggplot2)
  library(SHAPforxgboost)
})
# ** need to revise accordingly the path to your local clone of Just_universal **
source("~/liuyanguu/Just_universal/code/xgboost_cvtune.R")
source("~/liuyanguu/Just_universal/code/xgboost_cv_RFE.R")

@@

# point to cache: 
ssd_cache = new_cache(path = "/scratch/cache/aeronet_drake") 
```

>>>>

# Libraries
# if needed, update drake
if(packageVersion("drake")<7.4) install.packages("drake")
suppressPackageStartupMessages({
  library(sf)
  library(magrittr)
  library(drake)
  library(data.table)
  library(fst)
  library(future)
  library(here)
  library(nngeo)
  library(ggplot2)
  library(SHAPforxgboost)
})
# ** need to revise accordingly the path to your local clone of Just_universal **
source("~/liuyanguu/Just_universal/code/xgboost_cvtune.R")
source("~/liuyanguu/Just_universal/code/xgboost_cv_RFE.R")

@@

# point to cache: 
ssd_cache = drake_cache(path = "/scratch/cache/aeronet_drake") 
```
